Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-04 manuscript/draft.Rmd
fix dietze spelling

![**A.** Model predictions for route 72035 when all observers are treated the
same (black points). **B.** Model predictions for the same route when accounting
for systematic differences between observers (represented by the points'
colors). In this example most models are made more robust to observer turnover.
Note that the "naive" model is less sensitive to observer turnover, and does not
benefit as much from modeling it.](../figures/observer_predictions.png)

@@

When comparing different methods for forecasting our results demonstrate the
importance of considering uncertainty [Box 1; @clark2001; @dietz2016]. Previous
comparisons between stacked SDMs and macroecological models reported that the
methods yielded equivalent results for forecasting diversity [@algar2009;
@distler2015]. While our results support this equivalence for point estimates,
they also show that stacked SDMs dramatically underestimate the range of
possible outcomes; after ten years, more than a third of the observed richness
values fell outside the stacked SDMs' 95% prediction intervals. Consistent with
@harris2015 and @warton2015, we found that JSDMs' wider prediction intervals
enabled them to avoid this problem. Macroecological models appear to share this
advantage, while being considerably easier to implement.

>>>>

![**A.** Model predictions for Pennsylvania route 35 when all observers are
treated the same (black points). **B.** Model predictions for the same route
when accounting for systematic differences between observers (represented by the
points' colors). In this example most models are made more robust to observer
turnover. Note that the "naive" model is less sensitive to observer turnover,
and does not benefit as much from modeling
it.](../figures/observer_predictions.png)

@@

When comparing different methods for forecasting our results demonstrate the
importance of considering uncertainty [Box 1; @clark2001; @dietze2016]. Previous
comparisons between stacked SDMs and macroecological models reported that the
methods yielded equivalent results for forecasting diversity [@algar2009;
@distler2015]. While our results support this equivalence for point estimates,
they also show that stacked SDMs dramatically underestimate the range of
possible outcomes; after ten years, more than a third of the observed richness
values fell outside the stacked SDMs' 95% prediction intervals. Consistent with
@harris2015 and @warton2015, we found that JSDMs' wider prediction intervals
enabled them to avoid this problem. Macroecological models appear to share this
advantage, while being considerably easier to implement.
